---
title: "pinsLabkey"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pinsLabkey}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The pinsLabkey package provides a wrapper around [pins](https://pins.rstudio.com/) to use pins on a [LabKey](https://www.labkey.com/) board, using the [Rlabkey](https://github.com/LabKey/labkey-api-r) package. 

## Usage

To read or write a pin from a LabKey board, you must first create a board object. Provide the folder and folder subdirectory on the LabKey board to use. If not specified, the folder subdirectory "pins" will be used. 

Notes on credentials. If you are reading/writing to a non-public board, you may need to provide credentials too access pins on a LabKey board. Provide a LabKey api key using the environment variable `LABKEY_API_KEY`.

```{r setup}
library(pinsLabkey)
# library(Rlabkey)

# easiest if alias is provided
board <- board_labkey(board_alias = "pins-test", # becomes 'labkey-pins-test in cache
                      base_url = "https://learn.labkey.com/",
                      folder = "LabKey_Board/",
                      subdir = "pins")
```

Pin data to a LabKey board using pin_write(): 

```{r}
board %>% pin_write(mtcars, "mtcars")
```

And retrieve pinned data from a LabKey board with pin_read(): 

```{r}
board %>% pin_read("mtcars")
```

You can also list the available pins on the LabKey board and pin versions: 

```{r}
board %>% pin_list()
board %>% pin_versions(name = "mtcars")
```

If there are multiple versions of the same pin, these can be retrieved by version or hash. 

```{r}
board %>% pin_write(head(mtcars), "mtcars")
board %>% pin_versions(name = "mtcars")
board %>% pin_read("mtcars", hash = "a800d")
```


Pins can be deleted by name (all versions deleted) or by version. 

```{r}
versions <- pin_versions(board, name = "mtcars")
board %>% pin_version_delete(name = "mtcars", version = versions$version[1])
board %>% pin_versions(name = "mtcars")
board %>% pin_delete(name = "mtcars")
board %>% pin_list()
```
