---
title: "pinsLabkey"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pinsLabkey}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The pinsLabkey package provides a wrapper around [pins](https://pins.rstudio.com/) to use pins on a [LabKey](https://www.labkey.com/) board, using the [Rlabkey](https://github.com/LabKey/labkey-api-r) package. 

## Usage

To read or write a pin from a LabKey board, you must first create a board object. Provide the folder and folder subdirectory on the LabKey board to use. If not specified, the folder subdirectory "pins" will be used. 

Notes on credentials: If you are reading/writing to a non-public board, you may need to provide credentials to access pins on a LabKey board. Provide a LabKey api key using the environment variable `LABKEY_API_KEY`.

```{r}
library(pinsLabkey)

# create a board object
board <- board_labkey(
  board_alias = "pins-test", # becomes 'labkey-pins-test in cache
  base_url = "https://learn.labkey.com/",
  folder = "LabKey_Board/",
  subdir = "pins_test"
)
```

Pin data to a LabKey board using `pin_write()`: 

```{r}
board %>% pins::pin_write(mtcars, "mtcars")
```

And retrieve pinned data from a LabKey board with `pin_read()`: 

```{r}
board %>% pin_read("mtcars")
```

If there are multiple versions of the same pin, these can be retrieved by version (or hash for the latest version)

```{r}
board %>% pin_write(head(mtcars), "mtcars")
versions <- board %>% pin_versions(name = "mtcars")
versions
board %>% pin_read("mtcars", version = versions$version[1])
```

You can also list the available pins on the LabKey board:

```{r}
board %>% pin_list()
```

Pins can be deleted by version: 

```{r}
board %>% pin_version_delete(name = "mtcars", version = versions$version[1])
board %>% pin_versions(name = "mtcars")
```

Or by name to delete all versions of a pin: 

```{r}
board %>% pin_read(name = "mtcars")
board %>% pin_delete(name = "mtcars")
board %>% pin_list()
```
